Parallel multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-12-13 hpmoon-coor.tex
Some choices explained. Closes #2

\subsection{Adaptive coevolution with overlapping islands (A)} 
As in the previous method, the sections to address are overlapped, but instead using one extra section on each side of the $p$ section ($p+1$ and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$), being $c$ a value depending on the number of islands. As a first approach to automatically calculate this value the results shown in \citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that work, the overlapped method ($c=1$) obtained better results when the number of islands were $>$8. So, we have used the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap. Therefore, when $P=8$ then $c=0$ (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so on. Figure \ref{fig:adaptive} explains this method.

@@

These metrics have been used extensively, especially in some of the papers presented in Section 2.

>>>>

\subsection{Adaptive coevolution with overlapping islands (A)} 
As in the previous method, the sections to address are overlapped, but instead using one extra section on each side of the $p$ section ($p+1$ and $p-1$), it uses $c$ fragments on each side ($p+c$ and $p-c$), being $c$ a value depending on the number of islands. As a first approach to automatically calculate this value the results shown in \citep{Garcia16hpmoon} have been used as a base to obtain $c$. In that work, the overlapped method ($c=1$) obtained better results when the number of islands were $>$8. On the contrary, when the number of islands is small, no overlapping is necessary. So, we have used this knowledge to create the formula $c=round(0.2*P-1)/2$ to calculate the extra sections to overlap. Therefore, when $P=8$ then $c=0$ (equivalent to D), when $P=16$ then $c=1$ (equivalent to O), and so on. Figure \ref{fig:adaptive} explains this method.

@@

We have chosen those metrics because they have been used extensively, especially in some of the papers presented in Section 2 \cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous}.
